### 2017-03-07 writing/paper/sections/coincidences.tex
Make Changes suggest by Michael

\begin{figure}
\begin{equation*}
%\adda{\pattern{}{2,3,1}{0/0,1/0,1/3,
%                        3/0,3/1,3/3}}{(1,1)}
p = \pattern{}{1,2}{0/1,2/2} \quad
p^\boksrightup{2,1}
= \pattern{}{1,3,2}{0/1,0/2,2/2,2/3,3/1,3/2,3/3}
\end{equation*}
\caption{The result of inserting a point into \(p=(12,\{(0,1),(2,2)\})\)}
\label{fig:addp}
\end{figure}

\begin{definition}
Let \(p=(\tau,R)\) be a mesh pattern of length \(n\) such that \(\boks{i,j}\notin R\). We define
a mesh pattern \(p^{\boks{i,j}_a} = (\tau^\prime,R^\prime)\) (\(p^{\boks{i,j}_d}\)) of length \(n+2\)
as the pattern where an ascent (descent) is \emph{inserted} into the box \(\boks{i,j}\) in \(G(p)\).
Formally the new underlying classical pattern is defined by
\begin{equation*}
\tau^\prime(k) = \begin{cases}
    j+t & \text{if } k = i+t,t\in\{1,2\}\\
    \tau(k) & \text{if } \tau(k)\le j \text{ and }k\le i\\
    \tau(k)+2 & \text{if } \tau(k)> j \text{ and }k\le i\\
    \tau(k-2) & \text{if } \tau(k)\le j \text{ and }k> i+2\\
    \tau(k-2)+2 & \text{if } \tau(k)> j \text{ and }k> i+2\\
\end{cases}
\end{equation*}
The ordering of the top branch determines whether an ascent(or descent) is added.
The mesh becomes
\begin{equation*}
\begin{aligned}
R^\prime=&\{\boks{k,\ell}\mid k\le i, \ell\le j, \boks{k,\ell}\in R\} \cup\\
&\{\boks{k,\ell}\mid k\le i, \ell > j, \boks{k,\ell-2}\in R\}\cup\\
&\{\boks{k,\ell}\mid k > i, \ell \le j, \boks{k-2,\ell}\in R\}\cup\\
&\{\boks{k,\ell}\mid k > i, \ell > j, \boks{k-2,\ell-2}\in R\}\cup\\
&\{\boks{i,j+1},\boks{i+1,j},\boks{i+1,j+1},\boks{i+1,j+2},\boks{i+2,j+1}\}
\end{aligned}
\end{equation*}
\end{definition}
An example of adding an ascent to a mesh pattern can be seen in \FigureRef{fig:adda}.
\begin{figure}
\begin{equation*}
p = \pattern{}{2,3,1}{0/0,1/0,1/3,
                      3/0,3/1,3/3} \quad
p^{\boks{1,1}_a}= \pattern{}{4,2,3,5,1}{0/0,
                        1/0,1/2,1/5,
                        2/0,2/1,2/2,2/3,2/5,
                        3/0,3/2,3/5,
                        5/0,5/1,5/2,5/3,5/5}
\end{equation*}
\caption{The result of inserting an ascent into \(p=(231,\{(0,0),(1,0),(1,3),(3,0),(3,1),(3,3)\})\)}
\label{fig:adda}
\end{figure}

@@

All coincidence classes of \(\av{\{\perm{3,2,1}, \mperm{2,1}{R}\}}\) can be
explained by application of \PropositionRef{prop:dom1}. By experimentation
we see that there are at least \(29\) coincidence classes, and all of these
coincidences are explained by this Proposition.

@@

\subsection{Equivalence classes of Av(\{231, (21, \textit{R})\}).}
By application of \PropositionRef{prop:dom1} we obtain \(43\) coincidence
classes. Experimentation shows that there are in fact at least \(39\) coincidence
classes, for example the following two patterns are coincident in
\(\av{\perm{2,3,1}}\) but this is not explained by \PropositionRef{prop:dom1}.
\begin{equation*}
    m_1 = \pattern{}{2,1}{0/0,0/1,0/2,1/0,2/1} \text{ and } m_2 = \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,2/1}
\end{equation*}

@@

    Now consider if the region is non-empty, by \LemmaRef{lem:incdec} and
    condition~\ref{prop:dom2:condc} of the proposition this region must contain
    a decreasing subsequence.
    We can choose the topmost point in the region to replace the corresponding
    point in the mesh pattern and the points from the subsequence are now in
    the box southeast of the point. The other conditions allow this to be done
    without points being present in regions that were shaded. Hence there are no
    points in the region corresponding to the box \((a,b)\) in the mesh
    pattern, and therefore we can shade this region. This implies that every
    occurrence of \(m_1\) in \(\av{\pi}\) is in fact an occurrence of \(m_2\)
    so \(\av{\{\pi,m_2\}} \subseteq \av{\{\pi,m_1\}}\).

    Similar arguments satisfy the remainder of the branches.
\end{proof}

@@

By taking the First Dominating Pattern Rule and the Second Dominating Pattern
Rule together coincidences of classes of the form \(\av{\{\perm{2,3,1},\mperm{2,1}{R}\}}\)
are fully explained, obtaining 39 coincidence classes of mesh patterns.

@@

By application of this rule we can reduce the number of classes in
\(\av{\{\perm{2,3,1},(\perm{1,2}, R)\}}\) to \(56\).

@@

In order to prove this coincidence we will proceed by mathematical
induction on the number of points in region corresponding to the middle box.
We call this number \(n\).
\begin{description}
    \item [Base Case \((n=0)\)] The base case holds since we can freely shade the
        box if it contains no points.
    \item [Inductive Hypothesis \((n=k)\)] Suppose that we can find an occurrence
        of the second pattern if we have an occurrence of the first with \(k\) points
        in the middle box.
    \item [Inductive Step \((n=k+1)\)] Suppose that we have \((k+1)\) points in
        the middle box. Choose the bottom most point in the middle box, this gives the
        mesh pattern
     \begin{equation*}
        \begin{tikzpicture}[scale=0.5]
            \modpattern[5]{}{1,2,3}{0/1,0/2,0/3,1/1,2/1,3/0,3/1,3/2}
            \draw (2.5,0.5) node {\(X\)};
        \end{tikzpicture}
    \end{equation*}
        Now we need to consider the box labelled \(X\). If this box is empty then
        we have an occurrence of \(m_2\) and are done. If this box contains
        any points then we gain some extra shading on the mesh pattern
        due to the dominating pattern
     \begin{equation*}
        \begin{tikzpicture}[scale=0.5]
            \modpattern[5]{2,3}{1,2,3}{0/1,0/2,0/3,1/1,1/2,1/3,2/1,3/0,3/1,3/2}
            \filldraw (2.5,0.5) circle (4 pt);
        \end{tikzpicture}
    \end{equation*}
        The two highlighted points form an occurrence of \(m_1\) with \(k\)
        points in the middle box, and thus by the Inductive Hypothesis we
        are done.
\end{description}
By induction we have that every occurrence of \(m_1\) leads to an occurrence of \(m_2\)
and by \NoteRef{not:downcmesh} every occurrence of \(m_2\) is an occurrence of
\(m_1\) so the two patterns are coincident.
This argument applies to another two pairs of classes. Therefore in
total in \(\av{\perm{3,2,1}, \mperm{1,2}{R}}\) there are \(213\) coincidence
classes.

>>>>

\begin{figure}
\begin{equation*}
%\adda{\pattern{}{2,3,1}{0/0,1/0,1/3,
%                        3/0,3/1,3/3}}{(1,1)}
p = \pattern{}{1,2}{0/1,2/2} \quad
p^\boks{2,1}= \pattern{}{1,3,2}{0/1,0/2,2/3,3/3}
\quad
p^\boksup{2,1}
= \pattern{}{1,3,2}{0/1,0/2,2/2,2/3,3/2,3/3}
\end{equation*}
\caption{The result of inserting a point into \(p=(12,\{(0,1),(2,2)\})\)}
\label{fig:addp}
\end{figure}

\begin{definition}
Let \(p=(\tau,R)\) be a mesh pattern of length \(n\) such that \(\boks{i,j}\notin R\). We define
a mesh pattern \(p^{\boks{i,j}_a} = (\tau^\prime,R^\prime)\) (\(p^{\boks{i,j}_d}\)) of length \(n+2\)
as the pattern where an ascent (descent) is \emph{inserted} into the box \(\boks{i,j}\) in \(G(p)\).
Formally the new underlying classical pattern is defined by
\begin{equation*}
\tau^\prime(k) = \begin{cases}
    j+t & \text{if } k = i+t,t\in\{1,2\}\\
    \tau(k) & \text{if } \tau(k)\le j \text{ and }k\le i\\
    \tau(k)+2 & \text{if } \tau(k)> j \text{ and }k\le i\\
    \tau(k-2) & \text{if } \tau(k)\le j \text{ and }k> i+2\\
    \tau(k-2)+2 & \text{if } \tau(k)> j \text{ and }k> i+2\\
\end{cases}
\end{equation*}
The ordering of the top branch determines whether an ascent(or descent) is added.
The mesh becomes
\begin{equation*}
\begin{aligned}
R^\prime=&\{\boks{k,\ell}\mid k\le i, \ell\le j, \boks{k,\ell}\in R\} \cup\\
&\{\boks{k,\ell}\mid k\le i, \ell > j, \boks{k,\ell-2}\in R\}\cup\\
&\{\boks{k,\ell}\mid k > i, \ell \le j, \boks{k-2,\ell}\in R\}\cup\\
&\{\boks{k,\ell}\mid k > i, \ell > j, \boks{k-2,\ell-2}\in R\}\cup\\
&\{\boks{i+1,j},\boks{i+1,j+1},\boks{i+1,j+2}\}
\end{aligned}
\end{equation*}
\end{definition}
An example of adding an ascent to a mesh pattern can be seen in \FigureRef{fig:adda}.
\begin{figure}
\begin{equation*}
p = \pattern{}{2,3,1}{0/0,1/0,1/3,
                      3/0,3/1,3/3} \quad
p^{\boks{1,1}_a}= \pattern{}{4,2,3,5,1}{0/0,
                        1/0,1/5,
                        2/0,2/1,2/2,2/3,2/5,
                        3/0,3/5,
                        5/0,5/1,5/2,5/3,5/5}
\end{equation*}
\caption{The result of inserting an ascent into \(p=(231,\{(0,0),(1,0),(1,3),(3,0),(3,1),(3,3)\})\)}
\label{fig:adda}
\end{figure}

@@

All coincidence classes of \(\av{\{\perm{3,2,1}, \mperm{2,1}{R}\}}\) can be
explained by application of \PropositionRef{prop:dom1}. Thus explaining the
29 experimental coincidence classes opserved.

@@

\subsection{Equivalence classes of Av(\{231, (21, \textit{R})\}).}
By application of \PropositionRef{prop:dom1} we obtain \(43\) coincidence
classes. Experimentation shows that there are in fact at least \(39\) coincidence
classes, for example the following two patterns seem to be coincident in
\(\av{\perm{2,3,1}}\) but this is not explained by \PropositionRef{prop:dom1}.
\begin{equation*}
    m_1 = \pattern{}{2,1}{0/0,0/1,0/2,1/0,2/1} \text{ and } m_2 = \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,2/1}
\end{equation*}

@@

    If the region is non-empty, then by \LemmaRef{lem:incdec} and
    condition~\ref{prop:dom2:condc} of the proposition it must contain
    a decreasing subsequence.
    We can choose the topmost point in the region to replace the corresponding
    point in the mesh pattern and the points from the subsequence are now in
    the box southeast of the point. The other conditions allow this to be done
    without points being present in regions that were shaded. Hence there are no
    points in the region corresponding to the box \((a,b)\) in the mesh
    pattern, and therefore we can shade this region. This implies that every
    occurrence of \(m_1\) in \(\av{\pi}\) is in fact an occurrence of \(m_2\)
    so \(\av{\{\pi,m_2\}} \subseteq \av{\{\pi,m_1\}}\).

    Similar arguments cover the remainder of the branches.
\end{proof}

@@

By taking the First Dominating Pattern Rule and the Second Dominating Pattern
Rule together coincidences of classes of the form \(\av{\{\perm{2,3,1},\mperm{2,1}{R}\}}\)
are fully explained, obtaining 39 coincidence classes of mesh patterns, confirming experimental
observations.

@@

By application of this rule we can reduce the number of classes in
\(\av{\{\perm{2,3,1},(\perm{1,2}, R)\}}\) to \(56\), which coincides with the 
56 classes observed through experimentation

@@

In order to prove this coincidence we will proceed by mathematical
induction on the number of points in region corresponding to the middle box.
We call this number \(n\).
\begin{description}
    \item [Base Case \((n=0)\)] The base case holds since we can freely shade the
        box if it contains no points.
    \item [Inductive Hypothesis \((n=k)\)] Suppose that we can find an occurrence
        of the second pattern if we have an occurrence of the first with \(k\) points
        in the middle box.
    \item [Inductive Step \((n=k+1)\)] Suppose that we have \((k+1)\) points in
        the middle box. Choose the bottom most point in the middle box, this gives the
        mesh pattern
     \begin{equation*}
        \begin{tikzpicture}[scale=0.5]
            \modpattern[5]{}{1,2,3}{0/1,0/2,0/3,1/1,2/1,3/0,3/1,3/2}
            \draw (2.5,0.5) node {\(X\)};
        \end{tikzpicture}
    \end{equation*}
        Now we need to consider the box labelled \(X\). If this box is empty then
        we have an occurrence of \(m_2\) and are done. If this box contains
        any points then we gain some extra shading on the mesh pattern
        as any points in these boxes would create an occurrence of the dominating pattern \(\perm{2,3,1}\)
     \begin{equation*}
        \begin{tikzpicture}[scale=0.5]
            \modpattern[5]{2,3}{1,2,3}{0/1,0/2,0/3,1/1,1/2,1/3,2/1,3/0,3/1,3/2}
            \filldraw (2.5,0.5) circle (4 pt);
        \end{tikzpicture}
    \end{equation*}
        The two highlighted points form an occurrence of \(m_1\) with \(k\)
        points in the middle box, and thus by the Inductive Hypothesis we
        are done.
\end{description}
By induction we have that every occurrence of \(m_1\) leads to an occurrence of \(m_2\)
and by \NoteRef{not:downcmesh} every occurrence of \(m_2\) is an occurrence of
\(m_1\) so the two patterns are coincident.
This argument applies to another two pairs of classes. Therefore in
total in \(\av{\perm{3,2,1}, \mperm{1,2}{R}}\) there are \(213\) coincidence
classes.

### 2017-03-07 writing/paper/sections/meshpatterns.tex
Make Changes suggest by Michael

The definition of order isomorphism allows us to give the meaning of containment for classical
permutation patterns.
\begin{definition}
    A permutation \(\pi\in\mathfrak{S}_n\) contains the pattern \(\sigma\in\mathfrak{S}_k\) (\mbox{denoted} 
    \(\sigma \preceq \pi\)) if there is some subsequence of indices of \(\pi, i_1i_2\dotsm{}i_k\)
    such that the sequence \(\pi(i_1)\pi(i_2)\dotsm\pi(i_k)\) is order isomorphic to
    \(\sigma(1)\sigma(2)\dotsm\sigma(k)\). If \(\pi\) does not contain \(\sigma\), we say that 
    \(\pi\) \emph{avoids} \(\sigma\).
\end{definition}
\begin{example}
\label{ex:contexmpl}
The permutation \(\pi = \perm{2,4,1,5,3}\) contains the pattern 
\(\sigma = \perm{2,3,1}\), since the second, fourth and fifth elements (\(453\)) are order 
isomorphic to \(\perm{231}\), it also contains the occurrence \(241\). The permutation 
\(\perm{2,4,1,5,3}\) avoids the pattern \(\perm{3,2,1}\).
\end{example}

@@

@@

\begin{definition}
A \emph{mesh pattern} is a pair
\begin{equation*}
    p = (\tau,R)\text{ with } \tau \in \mathfrak{S}_k \text{ and } R \subseteq [0,k]\times [0,k].
\end{equation*}
\end{definition}
We define containment (denoted \(p\preceq \pi\)), and avoidance, of the pattern \(p\) in the permutation
\(\pi\) on mesh patterns analogously to classical containment, and avoidance,
of \(\tau\) in \(\pi\) with the additional restrictions on the relative
position of the occurrence of \(\tau\) in \(\pi\). These restrictions say that
no elements of \(\pi\) are allowed in the regions of the plot corresponding
to shaded boxes in the mesh. These boxes are denoted by \(\boks{i,j}\), where the point \((i,j)\) is
the lower left corner of the box.

@@

\noindent Firstly, \(\omega\) is an occurrence of \(\pi\) in the classical sense
  \begin{enumerate}[i.]
    \item \(\omega = \{(\alpha(i),\beta(j)):(i,j)\in G(\tau)\}\)
  \end{enumerate}\saveenum
  Define \(R_{ij} = [\alpha(i)+1,\alpha(i+1)-1]\times[\beta(j)+1,\beta(j+1)-1]\)
   for \(i,j\in[0,k]\) where \(\alpha(0)=\beta(0)=0\) and \(\alpha(k+1)=\beta(k+1)=n+1\). Then
   the second condition is
  \begin{enumerate}[i.]\resetenum
  \item if \(\boks{i,j} \in R \text{ then } R_{ij} \cap G(\pi) = \emptyset\)
\end{enumerate}
We call \(R_{ij}\) the region corresponding to \(\boks{i,j}\).
We define containment of a mesh pattern \(p\) in another mesh pattern \(q\) as above,
with the additional condition that if \(\boks{i,j}\in R\text{ then } R_{ij}\) is
contained in the mesh set of \(q\), in this case we call \(p\) a \emph{subpattern}
of \(q\).
\begin{definition}
A mesh pattern \(q=(\kappa,T)\) \emph{contains} a mesh pattern \(p=(\tau,R)\) as a \emph{subpattern}
if \(\kappa\) contains \(\tau\) and \(\left(\bigcup_{\boks{i,j}\in R} R_{ij}\right)\subseteq T\).
\end{definition}

>>>>

The definition of order isomorphism allows us to give the meaning of containment for classical
permutation patterns.
\begin{definition}
    A permutation \(\pi\in\mathfrak{S}_n\) contains the pattern \(\sigma\in\mathfrak{S}_k\) (\mbox{denoted} 
    \(\sigma \preceq \pi\)) if there is some sequence\( i_1,i_2,\dotsm{},i_k\)
    such that \(1\le i_1<i_2<\dotsm<i_k\le n\) and the sequence \(\pi(i_1)\pi(i_2)\dotsm\pi(i_k)\) is order isomorphic to
    \(\sigma(1)\sigma(2)\dotsm\sigma(k)\). If \(\pi\) does not contain \(\sigma\), we say that 
    \(\pi\) \emph{avoids} \(\sigma\).
\end{definition}
\begin{example}
\label{ex:contexmpl}
The permutation \(\pi = \perm{2,4,1,5,3}\) contains the pattern 
\(\sigma = \perm{2,3,1}\), since the second, fourth and fifth elements (\(453\)) are order 
isomorphic to \(\perm{231}\), it also contains the occurrence \(241\) of the sam pattern. The permutation 
\(\perm{2,4,1,5,3}\) avoids the pattern \(\perm{3,2,1}\).
\end{example}

@@

The boxes in the plot of a permutation are denoted by \(\boks{i,j}\), where the point \((i,j)\) is
the lower left corner of the box.

@@

\begin{definition}
A \emph{mesh pattern} is a pair
\begin{equation*}
    p = (\tau,R)\text{ with } \tau \in \mathfrak{S}_k \text{ and } R \subseteq [0,k]\times [0,k].
\end{equation*}
\end{definition}

@@

\noindent Firstly, \(\omega\) is an occurrence of \(\tau\) in the classical sense
  \begin{enumerate}[i.]
    \item \(\omega = \{(\alpha(i),\beta(j)):(i,j)\in G(\tau)\}\)
  \end{enumerate}\saveenum
  Define \(R_{ij} = [\alpha(i)+1,\alpha(i+1)-1]\times[\beta(j)+1,\beta(j+1)-1]\)
   for \(i,j\in[0,k]\) where \(\alpha(0)=\beta(0)=0\) and \(\alpha(k+1)=\beta(k+1)=n+1\). Then
   the second condition is
  \begin{enumerate}[i.]\resetenum
  \item if \(\boks{i,j} \in R \text{ then } R_{ij} \cap G(\pi) = \emptyset\)
\end{enumerate}
We call \(R_{ij}\) the region corresponding to \(\boks{i,j}\).
We define containment of a mesh pattern \(p\) in another mesh pattern \(q\) as above,
with the additional condition that if \(\boks{i,j}\in R\text{ then } R_{ij}\) is
contained in the mesh set of \(q\), in this case we call \(p\) a \emph{subpattern}
of \(q\).
\begin{definition}
A mesh pattern \(q=(\kappa,T)\) \emph{contains} a mesh pattern \(p=(\tau,R)\) as a \emph{subpattern}
if \(\kappa\) contains \(\tau\) and \(\left(\bigcup_{\boks{i,j}\in R} R_{ij}\right)\subseteq T\).
\end{definition}

### 2017-03-07 writing/paper/sections/wilf.tex
Make Changes suggest by Michael

Wilf-equivalence is an important aspect to study in the field of permutation
patterns. If two patterns \(\pi\) and \(\sigma\) are said to be Wilf-equivalent
if their avoidance sets have the same size at each length. More formally:

@@

Wilf-equivalence is of interest due to the fact that if two permutation classes
are enumerated in the same way then there should exist a bijection between
them, and therefore any combinatorial object they represent.

@@

When examining Wilf-equivalences we can use a number of symmetries to reduce
the amount of work required. It can be seen that the reverse, complement
and inverse operations (see \FigureRef{fig:symm}) preserve enumeration, and
therefore these classes are trivially
Wilf-equivalent.
\begin{figure}[!htb]
\begin{align*}
    \rev{\textpattern{}{2,3,1}{}} &= \textpattern{}{1,3,2}{}\\
    \com{\textpattern{}{2,3,1}{}} &= \textpattern{}{2,1,3}{}\\
    \inv{\textpattern{}{2,3,1}{}} &= \textpattern{}{3,1,2}{}
\end{align*}
\caption{The operations reverse, complement and inverse for the pattern 231}
\label{fig:symm}
\end{figure}

@@

Throughout this section we will consider Wilf-equivalences of patterns
whilst avoiding the \emph{dominating pattern} \(\perm{2,3,1}\). We will
use \(\mathcal{C}\) to denote \(\av{\perm{2,3,1}}\) and \(C(x)\) will
be the usual Catalan generating function satisfying \(C(x) = 1 + xC(x)^2\).
This is easy to see by structural decomposition around the maximum, as
shown in \FigureRef{fig:decompmax}.

@@

\nextvar[\varfine]
It can be shown by use of \PropositionRef{prop:dom2} that the patterns
\textpattern{}{1}{0/0,1/1} and \(q_1 = \textpattern{}{1}{0/0,0/1,1/1}\) are
coincident. Consider the decomposition of a non-empty avoider of \(q_1\) in
\(\av{\perm{2,3,1}}\) around the maximum:
\begin{equation*}
    \scriptvar_1 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}
\end{equation*}
This can be explained succinctly by the fact that a permutation containing
\(q_1\) starts with it's maximum, by not allowing the lower-left section of the
\(\perm{2,3,1}\) avoider to be empty we prevent an occurrence from ever
happening.

Consider \(q_2 = \textpattern{}{1}{0/1,1/0,1/1}\), avoiding this pattern
means that a permutation does not end with it's maximum. We can perform a
similar
decomposition as before to get
\begin{equation*}
    \mathcal{\var}_2 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}}{}{}{\mathcal{C}\setminus\varepsilon}
\end{equation*}

@@

\nextvar[\varmaxl]
There is one pattern of length \(1\) still to consider. The pattern
\(r = \textpattern{}{1}{0/0,1/0,1/1}\) is avoided by all permutations
that do not end in their minimum. Considering the standard decomposition
of a \(\perm{2,3,1}\) avoider around the maximum we can see that an avoider
of \(r\) must fit into precisely one of the following two forms.
\begin{equation*}
    \scriptvar = \varepsilon \sqcup
    \underbrace{\decompmax{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}}_\text{Minimum comes before the maximum.} \sqcup
\underbrace{\decompmax{0/0,0/1,1/0}{}{}{}{\scriptstyle{\scriptvar\setminus\varepsilon}}}_\text{
        Minimum is after the maximum, minimum cannot be last.
    }
\end{equation*}
Therefore this particular class has generating function \(\var(x)\) satisfying
\begin{equation*}
    \var(x) = 1 + xC(x)(C(x)-1) + x(\var(x)-1)
\end{equation*}
Computing coefficients of this generating function gives
\begin{equation*}
    	1, 0, 1, 4, 13, 41, 131, 428, 1429, 4861, 16795,\dotsc
\tag{\href{https://oeis.org/A141364}{OEIS: A141364}}
\end{equation*}

@@

\begin{note}
  The avoiders of the pattern \(q = \mperm{\perm{2,3,1}}{(1,0),(1,1),(1,2),(1,3)},
\textpattern{}{2,3,1}{1/0,1/1,1/2,1/3}\) in \(\mathfrak{S}_n\) are in one-to-one correspondence with partitions
of \(\nrange{n}\) (\textcite[Prop.~2]{DBLP:journals/ejc/Claesson01})
\end{note}
We will call the least element in each block the \emph{block-bottom}, and note that all permutations
in \(\av{\perm{2,3,1}}\) also avoid this mesh pattern.

@@

In order to establish the remainder of the Wilf-equivalences of the form \(\av{231,p}\) where \(p\)
is a mesh pattern we can use similar methods to allow us to consolidate experimental classes into
actual classes.

>>>>

Wilf-equivalence is an important aspect to study in the field of permutation
patterns. Two patterns \(\pi\) and \(\sigma\) are said to be Wilf-equivalent
if their avoidance sets have the same size at each length. More formally:

@@

@@

When examining Wilf-equivalences we can use a number of symmetries to reduce
the amount of work required. It can be seen that the reverse, complement
and inverse operations (see \FigureRef{fig:symm}) preserve enumeration, and
therefore classes related by these symmetries are trivially
Wilf-equivalent.
\begin{figure}[!htb]
\begin{align*}
    \rev{\textpattern{}{2,3,1}{}} &= \textpattern{}{1,3,2}{}\\
    \com{\textpattern{}{2,3,1}{}} &= \textpattern{}{2,1,3}{}\\
    \inv{\textpattern{}{2,3,1}{}} &= \textpattern{}{3,1,2}{}
\end{align*}
\caption{The operations reverse, complement and inverse for the pattern 231}
\label{fig:symm}
\end{figure}

@@

Throughout this section we will consider Wilf-equivalences of patterns
whilst avoiding the \emph{dominating pattern} \(\perm{2,3,1}\). We will
use \(\mathcal{C}\) to denote \(\av{\perm{2,3,1}}\) and \(C(x)\) will
be the usual Catalan generating function satisfying \(C(x) = 1 + xC(x)^2\).
The fact that \(C(x)\) is teh generating function for \(\mathcal{C}\)
can be seen by structural decomposition around the maximum, as
shown in \FigureRef{fig:decompmax}.

@@

\nextvar[\varfine]
It can be shown by use of \PropositionRef{prop:dom2} that the patterns
\textpattern{}{1}{0/0,1/1} and \(q_1 = \textpattern{}{1}{0/0,0/1,1/1}\) are
coincident. Consider the decomposition of a non-empty avoider of \(q_1\) in
\(\av{\perm{2,3,1}}\) around the maximum:
\begin{equation*}
    \scriptvar_1 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}
\end{equation*}
This can be explained succinctly by the fact that a permutation containing
\(q_1\) starts with its maximum, by not allowing the lower-left section of the
\(\perm{2,3,1}\) avoider to be empty we prevent an occurrence from ever
happening.

Consider \(q_2 = \textpattern{}{1}{0/1,1/0,1/1}\), avoiding this pattern
means that a permutation does not end with its maximum. We can perform a
similar
decomposition as before to get
\begin{equation*}
    \mathcal{\var}_2 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}}{}{}{\mathcal{C}\setminus\varepsilon}
\end{equation*}

@@

\nextvar[\varmaxl]
There is one pattern of length \(1\) still to consider. The pattern
\(r = \textpattern{}{1}{0/0,1/0,1/1}\) is avoided by all permutations
that do not end in their minimum. Any avoider of \(\perm{2,3,1}\) that
ends in its minimum must be a decreasing sequence
Therefore this particular class has equation
\begin{equation*}
    \var(0) = 1, \var(x) = C(x)-1
\end{equation*}
Computing these values gives
\begin{equation*}
    	1, 0, 1, 4, 13, 41, 131, 428, 1429, 4861, 16795,\dotsc
\tag{\href{https://oeis.org/A141364}{OEIS: A141364}}
\end{equation*}

@@

\begin{definition} A \emph{Set Partition} of \(\nrange{n}\) is a set of non-empty subsets of \(\nrange{n}\)
such that \(\nrange{n}\) is a \emph{disjoint} union of these subsets.
\end{definition}

\begin{note}
  The avoiders of the pattern \(q = \mperm{\perm{2,3,1}}{(1,0),(1,1),(1,2),(1,3)},
\textpattern{}{2,3,1}{1/0,1/1,1/2,1/3}\) in \(\mathfrak{S}_n\) are in one-to-one correspondence with partitions
of \(\nrange{n}\) (\textcite[Prop.~2]{DBLP:journals/ejc/Claesson01})
\end{note}
\begin{example}
    The permutation \(\pi = \perm{5,4,2,1,3,9,6,8,7}\) corresponds to the
    partition \(\{\{5,4,2,1\},\{3\},\{9,6\},\{8,7\}\}\).
\end{example}

We will call the least element in each block the \emph{block-bottom}, and note that all permutations
in \(\av{\perm{2,3,1}}\) also avoid this mesh pattern.

@@

In order to establish the remainder of the Wilf-equivalences of the form \(\av{231,p}\) where \(p\)
is a mesh pattern we can use similar methods to allow us to consolidate experimental classes into
actual classes, these methods allow us to explain all 23 of the observed Wilf-classes seen in experimentation.
